---
title: "linear model from Web"
author: "ediaz16"
date: "Spring 2024"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```
# Introduction:

We will produce three equation models to get   
1. sim score baed on arm strength  
2. sim score based on arm grip strength  
3. sim score based on both arm and grip strength  

For each model we will predict sim for arm=88, grip=94

#Methods:

We have numerical responses (sim score) and numerical explanatory   variables (arm and grip strength ) so we use the numerical~numerical helper file    


## Model 1 SIM~ARMS

```{r}
model1.1 = lm(SIMS~ARM, data=data)
```

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

There is a positive relation between SIMS and ARM. If this were a perfect linear relation the points would be on a straight line. In this case the correlation are not on a strait line the there would be positive .8

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

This is the degree of correlation between ARM strength and SIMS score. A strong correlation is 1 and a weak correlation would be 0.

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The P value for coefficient of arm is .0000000000000002 is less than .05 
#### Predict at target point
```{r}
SIMSpredict= predict.lm(model.1, newdata= data.frame(ARM=88, GRIP=94), interval="confidence")
print(SIMSpredict)
```


The prediction for ARM 88 AND GRIP

#### scatterplot with model fit
  
```{r}
plot(SIMS~ARM,data=data)
abline(model.1,col="pink")
```

This is scatter plot with a function on it at ARM strength 88 the 95 percent confidence interval 0.49 and 0.92.

## Model 2 SIM~GRIP

### Now add in scatterplot


### Numerical results 


### Inferential  (Build model.2)
  

#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP


### Numerical results (cor)


```{r}
m = data.frame(data['GRIP'], data['ARM'], data['SIMS'])
cor(m)
```
  
Table shows that SIMS correlates with GRIP in a positive manner(0.64) and SIMS correlates with ARM also in a variables manner (0.69). This says these positive are useful in predicting SIMS


```{r}
plot(data$GRIP, data$ARM)
```


This plot shows GRIP and ARM are not independent so this is not necessarily a good model.  

### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 = lm(SIMS~GRIP+ARM, data = data)
print(summary(model.3))

```

#### predict model.3 at target point

```{r}
newPoint = data.frame(GRIP = 94, ARM = 88)
predict.lm(model.3, newPoint, interval = 'prediction')
```
  

The 95%  confidence interval is SIMS is between -2.13 and 2.43. Since this interval contains we do not have a very good prediction for SIMS. 

## Comparing nested models ANOVA Test

```{r}
anova(model.1,model.2)
```


### Model.1 vs Model.3

```{r}
anova(model.1,model.3)
```

P-value is 0.00000499, this is less than 0.05 so we conclude that model 3 is better than model .1 
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

